Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-20 icse/paper.tex
Conclusion
Ana

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt because it increases the size of the codebase and creates implicit dependencies between fragments of code. To remove such anti-patterns, the codebase should be refactored. Many tools aid in the detection process of such duplication problems, but failed to determine whether a duplicate fragment would improve the maintainability of the codebase when refactored.

We perform an exploratory study into the data that can be gathered from comparing before- and after snapshots of an automatically refactored system. We propose a tool to detect clones, analyze their context and automatically refactor a subset of them. We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the system. On the basis of these results, we decide which clones improve system design and thus should be refactored. %We identified a set of four factors that influence the maintainability impact of clones. The first is the size of the clone. The second is the relation between the code fragments in a clone. The third is whether the clone fragments create, modify or return data. The fourth is the amount of data that cloned fragments use. By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.
Given these maintainability influencing factors and their effect on the source code, we measure their impact over a large corpus of open source Java projects. %This results in a set of thresholds by which clones can be found that should be refactored to improve system maintainability.

We have identified that the size of the duplication problem is the biggest influencing factor on system maintainability. We found that the majority of duplicates spanning 29 or more tokens improve maintainability when refactored. Another maintainability influencing factor is the amount of data that needs to be passed to the merged location of the duplicate.
\end{abstract}

@@

In this study, we define a technique to detect clones such that they can be refactored. We evaluate the context of clones to determine which refactoring techniques are required to refactor clones in a specific context. We propose a tool for the automated refactoring of a subset of the detected clones, by extracting a new method out of duplicated code.

We use automated refactoring to compare the maintainability of the before- and after snapshots of a codebase for each duplication problem that is refactored. This gives us insight into whether clones detected by certain thresholds should be refactored to improve the maintainability of the codebase. This allows for more accurate suggestion of code clones for refactoring and can provide assistance in the refactoring process.

\section{Background}
This study researches an intersection of code clone and refactoring research. In this background section, we will explain the required background knowledge for terms used throughout this study.

\subsection{Code clone terminology}
In this study we use two concepts used to argue about code clones \cite{roy2007survey}:
\\ \textbf{Clone instance}: A single cloned fragment.
\\ \textbf{Clone class}: A set of similar clone instances.

@@

\subsection{Refactoring techniques}
In this section, we describe refactoring techniques that are relevant to refactoring code clones.

\subsubsection{Extract Method}
The most used technique to refactor duplicate code is ``Extract Method'' \cite{fowler2018refactoring}, which can be applied on code inside the body of a method. Several studies have already concluded that most duplication in source code is found in the body of methods \cite{lozano2007evaluating, white2016deep, bergman2004ethnographic}. The ``Extract Method'' technique moves functionality in method bodies to a new method. To reduce duplication, we extract the contents of a single clone instance to a new method and replace all clone instances by a call to this method.

\subsubsection{Move Method}
Often, ``Extract Method'' alone is not enough to refactor clones. This is because the extracted method has to be moved to a location that is accessible by all clone instances. To do this, we apply the ``Move Method'' refactoring technique \cite{fowler2018refactoring}. In object-oriented programming languages, we often move methods up in the inheritance structure of classes, also called ``Pull Up Method'' \cite{fowler2018refactoring}.

@@

\section{Conclusion}
We defined refactorable clones and created a tool to detect and refactor them. We measured statistical data with this tool over a large corpus of open-source Java software systems to get more information about the context of clones and how refactoring them influences system maintainability.

>>>>

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code. To remove such anti-patterns, the codebase should be refactored. Many tools aid in the detection process of such duplication problems, but fail to determine whether refactoring a duplicate fragment would improve the maintainability.

We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones improve system design and thus should be refactored. We evaluate our approach over a large corpus of open source Java projects.

We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use. we find that the size of a clone is the biggest influencing factor: the majority of duplicates spanning 29 or more tokens improve maintainability when refactored. The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the refactored method should not have more than 2 arguments. %The relation  %We identified a set of four factors that influence the maintainability impact of clones. The first is the size of the clone. The second is the relation between the code fragments in a clone. The third is whether the clone fragments create, modify or return data. The fourth is the amount of data that cloned fragments use. By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.
%Given these maintainability influencing factors and their effect on the source code, we measure their impact over a large corpus of open source Java projects. %This results in a set of thresholds by which clones can be found that should be refactored to improve system maintainability.

\end{abstract}

@@

In this study, we define a technique to detect clones such that they can be automatically refactored. We evaluate the relation and location of clones to determine which refactoring techniques are best suited. We introduce a tool that automatically refactors clones by extracting new methods out of duplicated code.

%TODO: Hint about results. Hint about methodology.
We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored. This gives us insight into whether clones detected by certain thresholds should be refactored to improve the maintainability of the codebase. This allows for more accurate suggestion of code clones for refactoring and can provide assistance in the refactoring process.

\section{Background}
Our study lies intersection of code clone and refactoring research. %In this background section, we explain the required background knowledge for terms used throughout this study.
We use two concepts to argue about code clones \cite{roy2007survey}:
\\ \textbf{Clone instance}: A single cloned fragment.
\\ \textbf{Clone class}: A set of similar clone instances.

@@

%\subsection{Refactoring techniques}
%In this section, we describe refactoring techniques that are relevant to refactoring code clones.
There are several refactoring techniques that are relevant to refactoring duplicated code:
\\ \textbf{Extract Method}: A common technique to refactor duplicate code is ``Extract Method'' \cite{fowler2018refactoring}, which can be applied on code inside the body of a method. This technique moves functionality in method bodies to a new method. To reduce duplication, we extract the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
\\ \textbf{Move Method}: Often, ``Extract Method'' alone is not enough to refactor clones. This is because the extracted method has to be moved to a location that is accessible by all clone instances. To do this, we apply the ``Move Method'' refactoring technique \cite{fowler2018refactoring}. In object-oriented programming languages, we often move methods up in the inheritance structure of classes, also called ``Pull Up Method'' \cite{fowler2018refactoring}.

@@

\section{Conclusion}
We defined automatically refactorable clones and created a tool to detect and refactor them. We measured statistical data with this tool over a large corpus of open-source Java software systems to get more information about the context of clones and how refactoring them influences system maintainability.
